### 2025-01-22 Thesis/Latex/Cover_page.tex
Updated thesis template with content for chapters

\thispagestyle{empty}
\begin{center}
	\begin{title}
		\textbf{\uppercase{ People's Democratic Republic of Algeria }} \\[0.2cm]
		\textbf{\uppercase{ MINISTRY OF HIGHER EDUCATION AND SCIENTIFIC RESEARCH }} \\[0.5cm]
		\textbf{\uppercase{ UNIVERSITY MUSTAPHA STAMBOULI OF MASCARA}}
	\end{title}
	\begin{figure}[H]
		\centering
		\label{logo_UD}\includegraphics[width=0.2\textwidth]{Figures/Logo_UM.jpg}
	\end{figure}
	{\large Faculty of Exact Sciences} \\[0.2cm]
	{\large Department of Computer Science} \\[0.2cm]
	{\large Dissertation } \\[0.2cm]
	{\ Submitted in partial fulfilment of the requirements for Doctorate degree in Computer Science} \\[0.2cm]
	{\large Option: Artificial Intelligence}\\[0.5cm]

    {\large Theme} \\[0.3cm]
%\hline	
%    \\[0.7cm]
	{\LARGE {\textbf{Neural Machine Translation for\\ Arabic Media Content}}}
	\\[0.7cm]
%\hline
%	 \\[0.5cm]

	{\large Presented by \textbf{Baligh BABAALI} }\\[0.5cm]

@@

	\it{Month  2024}
\end{center}

>>>>

\thispagestyle{empty}
\begin{center}
	\begin{title}
		\textbf{\uppercase{ People's Democratic Republic of Algeria }} \\[0.2cm]
		\textbf{\uppercase{ MINISTRY OF HIGHER EDUCATION AND SCIENTIFIC RESEARCH }} \\[0.5cm]
		\textbf{\uppercase{ UNIVERSITY MUSTAPHA STAMBOULI OF MASCARA}}
	\end{title}
	\begin{figure}[H]
		\centering
		\label{logo_UD}\includegraphics[width=0.2\textwidth]{Figures/Logo_UM.jpg}
	\end{figure}
	{\large Faculty of Exact Sciences} \\[0.2cm]
	{\large Department of Computer Science} \\[0.2cm]
	{\large Dissertation } \\[0.2cm]
	{\ Submitted in partial fulfilment of the requirements for Master degree in Computer Science} \\[0.2cm]
	{\large Option: Artificial Intelligence}\\[0.5cm]

    {\large Theme} \\[0.3cm]
%\hline	
%    \\[0.7cm]
	{\LARGE {\textbf{Enhancing Legal Information Access and \\ Reasoning  with  Retrieval-Augmented LLMs for Juridical Data}}}
	\\[0.7cm]
%\hline
%	 \\[0.5cm]

	{\large Presented by \textbf{Boudjenane Zoubida Asmaa} }\\[0.5cm]

@@

	\it{Month  2025}
\end{center}
